intRo

### 2015-08-10 presentations/jsm-2015/andee/index.Rmd
Presentations added to gh-pages

---
title: "intRo"
subtitle: "Statistical Analysis Software for Teaching"
author: "Andee Kaplan & Eric Hare"
date: "February 6, 2015"
output: ioslides_presentation
font-family: Helvetica
ioslides_presentation:
    logo: images/icon.png
    widescreen: true
---

@@

# Classroom

## `intRo` in the wild
 - `intRo` will be used this semester in STAT 201 and STAT 104
      - Homework assignments and labs will use `intRo` to emphasize class concepts
 - `intRo` is a supplement, not the focus of the class

## Homework 1
 - *Data*: OECD PISA Results in Focus report to assess the workforce readiness of 15-year old students
 - *Goal*: Explore graphically and numerically how the students perceive academics and math
 - `intRo` *Tasks*:
      1. Make a barchart of the variable Enjoy.Maths.
      1. Make a summary of the Enjoy.Maths variable. What proportion of these students agree or strongly agree with the statement "I enjoy mathematics"?
      2. Obtain a contingency table and mosaic plot of the relationship between Country and Enjoy.Maths. Print contingency tables with the **Count** and **Column Proportion** values.

# Our turn

@@

 - Dozens of students at accessing app at once
 - Simultaneous larger computations like printing results

>>>>

---
title: "intRo"
subtitle: "Statistical Analysis Software for Teaching"
author: "Andee Kaplan & Eric Hare"
date: "August 11, 2015"
output: ioslides_presentation
font-family: Helvetica
ioslides_presentation:
    logo: images/icon.png
    widescreen: true
---

@@

@@

 - Dozens of students accessing app at once
 - Simultaneous larger computations like printing results

### 2015-08-10 presentations/jsm-2015/eric/index.Rmd
Presentations added to gh-pages

---
title: "intRo"
subtitle: "Statistical Analysis Software for Teaching"
author: "Andee Kaplan & Eric Hare"
date: "January 12, 2015"
output: ioslides_presentation
font-family: Helvetica
ioslides_presentation:
    logo: images/icon.png
    widescreen: true
---

>>>>

---
title: "intRo"
subtitle: "Statistical Analysis Software for Teaching"
author: "Andee Kaplan & Eric Hare"
date: "August 12, 2015"
output: ioslides_presentation
font-family: Helvetica
ioslides_presentation:
    logo: images/icon.png
    widescreen: true
---
